FIXME

### 2013-08-28 writeups/proposal/proposal.tex
foo
Former-commit-id: 2d09514b331d087b9d249fe3b6e97d68f2ab2fc3 [formerly 238b1f973cf88ab3f4095687030d817ec640dc1b]
Former-commit-id: 2f4386587034d6f15ca04975f09a530885fb293e

The SNIF-ACT model uses the strength of association to measure the relationship between the words in a search query and the words contained in each query result.
A higher $S_{ji}$ between a query and a result means that the result is a better fit for the query, and that the user is more likely to click on that link.
The links that user chose in experimental testing were largely predictive of the strength of association measure.
The predictive power of the SNIF-ACT model went above and beyond what would be predicted by simply assuming that the user always clicks on the first link in the search results page.

>>>>

The SNIF-ACT model uses strength of association to measure the relationship between the words in a search query and the words contained in each query result.
A higher $S_{ji}$ between a query and a result means that the result is a better fit for the query, and that the user is more likely to click on that link.
The links that user chose in experimental testing were largely predictive of the strength of association measure.
The predictive power of the SNIF-ACT model went above and beyond what would be predicted by simply assuming that the user always clicks on the first link in the search results page.
